---
title: "AABP Survey Demographics"
author: "Whitney Knauer"
date: "today"
format: 
  html:
    toc: true 
    toc-float: true
    toc-location: right
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

```{r}
#| include: false
#| echo: false

library(tidyverse)
library(skimr)
library(dplyr)
library(ggplot2)
library(ggbeeswarm)
library(lme4)
library(car)
library(emmeans)
library(gmodels)
library(epiDisplay)
library(psych)
library(doBy)
library(ggpubr)
library(MASS)
library(pscl)
library(knitr)
library(RColorBrewer)
library(extrafont)

font_import()
loadfonts(device="win")

```

```{r}
#| include: false
#| echo: false

cha <- read_csv("data/CHA 10312023.csv") 

#excluding the folks who said non-binary or prefer not to say for gender. 
cha_mf <- cha %>%
  filter(Gender1 != "NO")
cha_mf$Indv <- factor(cha_mf$Indv, ordered = TRUE)
cha_mf$Pair <- factor(cha_mf$Pair, ordered = TRUE)
cha_mf$SmGrp <- factor(cha_mf$SmGrp, ordered = TRUE)
cha_mf$LargeGrp <- factor(cha_mf$LargeGrp, ordered = TRUE)
cha_mf$Dam <- factor(cha_mf$Dam, ordered = TRUE)
cha_mf$Nursecow <- factor(cha_mf$Nursecow, ordered = TRUE)

cha_mf$HouseIndv <- factor(cha_mf$HouseIndv, ordered = TRUE)
cha_mf$HousePair <- factor(cha_mf$HousePair, ordered = TRUE)
cha_mf$HouseSmlGrp <- factor(cha_mf$HouseSmlGrp, ordered = TRUE)
cha_mf$HouseLrgGrp <- factor(cha_mf$HouseLrgGrp, ordered = TRUE)
cha_mf$WithDam <- factor(cha_mf$WithDam, ordered = TRUE)
cha_mf$WithNurse <- factor(cha_mf$WithNurse, ordered = TRUE)

cha_mf$FeasibleINDVtoPAIR <- factor(cha_mf$FeasibleINDVtoPAIR, ordered = TRUE)
cha_mf$MostComm20y<- factor(cha_mf$MostComm20y, ordered = TRUE)
cha_mf$Country <- factor(cha_mf$Country)

# Viewing the first few rows of the filtered dataset
head(cha_mf)

# Use the subset function to create a new data set with a subset of variable "B"
usa <- subset(cha, Country == "US")
canada <- subset (cha, Country == "CAN")

# Print the new data set
print(usa)
print(canada)

    
glimpse (cha)

```

## Demographic Data

```{r}
#| echo: false

tab1(cha$VetSchool, sort.group = "decreasing", cum.percent = TRUE)
tab1(cha$GradYear, cum.percent=TRUE)
tab1(cha$TimefromGrad, sort.group = "alphabet", cum.percent= TRUE)
tab1(cha$PracticeRegion, sort.group = "decreasing", cum.percent = TRUE)
tab1(cha$Gender, sort.group = "decreasing", cum.percent = TRUE)
tab1(cha$Age, sort.group = "decreasing", cum.percent = TRUE)
tab1(cha$PrimaryEmployer, sort.group = "decreasing", cum.percent = TRUE)
tab1(cha$Country, sort.group = "decreasing", cum.percent = TRUE)
tab1(usa$Top10Dairy, sort.group = "decreasing", cum.percent = TRUE)
tab1(usa$DairyRegion, sort.group="decreasing", cum.percent=TRUE)
tab1(canada$DairyRegion, sort.group="decreasing", cum.percent=TRUE)

# Open a larger plotting device
pdf("my_plot.pdf", width = 10, height = 6)  # Adjust width and height as needed

# Create your plot
tab1(cha$`Type of Operations`, sort.group = "increasing")

# Close the plotting device when you're done
dev.off()

tab1(cha$DairyTime, sort.group = "decreasing", cum.percent = TRUE)






```

```{r}
#| echo: false

length(cha$Gender)
length(cha$Age)

CrossTable(cha$Gender, cha$Age, prop.r = FALSE, prop.c = FALSE)
CrossTable(cha$TimefromGrad, cha$Age, prop.r = FALSE, prop.c = FALSE)

cha |> 
  group_by(Gender1, Age1) |> 
  count()

25/(52+25)
64/(12+64)

52/(25+52)
12/(64+12)


```

```{r}
# Create a proportion table for a categorical variable
prop.table(table(cha$TimefromGrad))

# Calculate the proportions and convert to a data frame
prop_table <- prop.table(table(cha$TimefromGrad))
prop_table_df <- as.data.frame(prop_table)

# Rename the columns for clarity
colnames(prop_table_df) <- c("TimefromGrad", "Proportion")

# Print the data frame
print(prop_table_df)


table(cha$Gender, cha$TimefromGrad)



# Create a table of counts
count_table <- table(cha$TimefromGrad)

# Create a table of proportions
prop_table <- prop.table(count_table)

# Combine count and proportion tables into a data frame
result_table <- data.frame(Category = names(count_table), Count = as.numeric(count_table), Proportion = prop_table)

# Print the result table
print(result_table)


```

## How Ideal? Likert Question

### Overall

```{r}

#Likert Style Questions. 
#How ideal is individual housing

tab1(cha$Indv, cum.percent=TRUE)

#Likert Style Questions. 
#How ideal is pair housing

tab1(cha$Pair, cum.percent=TRUE)

#Likert Style Questions. 
#How ideal is small group housing

tab1(cha$SmGrp, cum.percent=TRUE)

#Likert Style Questions. 
#How ideal is Large Group housing

tab1(cha$LargeGrp, cum.percent=TRUE)

#Likert Style Questions. 
#How ideal is dam housing

tab1(cha$Dam, cum.percent=TRUE)

#Likert Style Questions. 
#How ideal is Nurse Cow housing

tab1(cha$Nursecow, cum.percent=TRUE)


```

Majority of respondents (76/157) still considered Individual housing to be the ideal way to raise dairy calves during the pre-weaning period. Then Pair, small group, large group, dam, nurse cow. Will be interesting to look at this parsed by different demographics.

### Ideal by Gender

```{r}

#Individual

# Using xtabs()
xtabs_gender_indv <- xtabs(~ Gender + Indv, cha)
# Display the tables
print(xtabs_gender_indv)

barplot(xtabs_gender_indv, beside = TRUE, col = c("red", "blue", "green","purple"))

# Adding labels to the bars
legend("center", legend = c("man", "non-binary", "prefer not to say", "woman"),
       fill = c("red", "blue", "green","purple"))


#Pair
xtabs_gender_pair <- xtabs(~ Gender + Pair, cha)
print(xtabs_gender_pair)
barplot(xtabs_gender_pair, beside = TRUE, col = c("red", "blue", "green","purple"))
legend("center", legend = c("man", "non-binary", "prefer not to say", "woman"),
       fill = c("red", "blue", "green","purple"))

#Small Group
xtabs_gender_small <- xtabs(~ Gender + SmGrp, cha)
print(xtabs_gender_small)
barplot(xtabs_gender_small, beside = TRUE, col = c("red", "blue", "green","purple"))
legend("center", legend = c("man", "non-binary", "prefer not to say", "woman"),
       fill = c("red", "blue", "green","purple"))

#Large Group
xtabs_gender_large <- xtabs(~ Gender + LargeGrp, cha)
print(xtabs_gender_large)
barplot(xtabs_gender_large, beside = TRUE, col = c("red", "blue", "green","purple"))
legend("center", legend = c("man", "non-binary", "prefer not to say", "woman"),
       fill = c("red", "blue", "green","purple"))

#Dam
xtabs_gender_dam <- xtabs(~ Gender + Dam, cha)
print(xtabs_gender_dam)
barplot(xtabs_gender_dam, beside = TRUE, col = c("red", "blue", "green","purple"))
legend("center", legend = c("man", "non-binary", "prefer not to say", "woman"),
       fill = c("red", "blue", "green","purple"))

#Nurse Cow
xtabs_gender_nurse <- xtabs(~ Gender + Nursecow, cha)
print(xtabs_gender_nurse)
barplot(xtabs_gender_nurse, beside = TRUE, col = c("red", "blue", "green","purple"))
legend("center", legend = c("man", "non-binary", "prefer not to say", "woman"),
       fill = c("red", "blue", "green","purple"))



```

### **Ideal by Gender1**

Non binary and prefer not to say were included in the same group.

```{r}

#Individual

# Using xtabs()
xtabs_gender_indv <- xtabs(~ Gender1 + Indv, cha)
# Display the tables
print(xtabs_gender_indv)

barplot(xtabs_gender_indv, beside = TRUE, col = c("red", "blue", "purple"))

# Adding labels to the bars
legend("center", legend = c("Man", "NO", "Woman"),
       fill = c("red", "blue", "purple"))


```

#### Ordinal Logistic by Gender1

```{r}
#trying ordinal logistic regression for these outcomes, using the cha_mf data set bc only want those who identify as either male or female. 

# Fit ordinal logistic regression model
model <- polr(Indv ~ Gender1, data = cha_mf, Hess=TRUE)
summary(model)
summary_model <- summary(model)

# Extract the z-value for Gender1Woman
z_value_gender1woman <- summary_model$coefficients["Gender1Woman", "t value"]

# Calculate the p-value using the cumulative distribution function of the standard normal distribution
p_value_gender1woman <- 2 * (1 - pnorm(abs(z_value_gender1woman)))

# Print the p-value
print(p_value_gender1woman)

#overall P value is 0.08


#Pair
xtabs_gender_pair <- xtabs(~ Gender1 + Pair, cha)
print(xtabs_gender_pair)
barplot(xtabs_gender_pair, beside = TRUE, col = c("red", "blue","purple"))
legend("center", legend = c("man", "NO", "woman"),
       fill = c("red", "blue","purple"))


model <- polr(Pair~ Gender1, data = cha_mf, Hess=TRUE)
summary(model)
summary_model <- summary(model)
z_value_gender1woman <- summary_model$coefficients["Gender1Woman", "t value"]
p_value_gender1woman <- 2 * (1 - pnorm(abs(z_value_gender1woman)))
print(p_value_gender1woman)

#overall p value = 0.44




#Small Group
xtabs_gender_small <- xtabs(~ Gender1 + SmGrp, cha)
print(xtabs_gender_small)
barplot(xtabs_gender_small, beside = TRUE, col = c("red", "blue","purple"))
legend("center", legend = c("man", "NO", "woman"),
       fill = c("red", "blue","purple"))


model <- polr(SmGrp ~ Gender1, data = cha_mf, Hess=TRUE)
summary(model)
summary_model <- summary(model)
z_value_gender1woman <- summary_model$coefficients["Gender1Woman", "t value"]
p_value_gender1woman <- 2 * (1 - pnorm(abs(z_value_gender1woman)))
print(p_value_gender1woman)

#overall p value = 0.27

#Large Group
xtabs_gender_large <- xtabs(~ Gender1 + LargeGrp, cha)
print(xtabs_gender_large)
barplot(xtabs_gender_large, beside = TRUE, col = c("red", "blue","purple"))
legend("center", legend = c("man", "NO", "woman"),
       fill = c("red", "blue","purple"))

model <- polr(LargeGrp~ Gender1, data = cha_mf, Hess=TRUE)
summary(model)
summary_model <- summary(model)
z_value_gender1woman <- summary_model$coefficients["Gender1Woman", "t value"]
p_value_gender1woman <- 2 * (1 - pnorm(abs(z_value_gender1woman)))
print(p_value_gender1woman)

#Overall difference between Men and Women in their acceptability of Large Group (p=0.02. Likely that women #found it a lot less ideal. Now how to look at different levels? What a cluster fuck. 


#Dam
xtabs_gender_dam <- xtabs(~ Gender1 + Dam, cha)
print(xtabs_gender_dam)
barplot(xtabs_gender_dam, beside = TRUE, col = c("red", "blue","purple"))
legend("center", legend = c("man", "NO", "woman"),
       fill = c("red", "blue","purple"))

model <- polr(Dam~ Gender1, data = cha_mf, Hess=TRUE)
summary(model)
summary_model <- summary(model)
z_value_gender1woman <- summary_model$coefficients["Gender1Woman", "t value"]
p_value_gender1woman <- 2 * (1 - pnorm(abs(z_value_gender1woman)))
print(p_value_gender1woman)

#Overall P value= 0.06



#Nurse Cow
xtabs_gender_nurse <- xtabs(~ Gender1 + Nursecow, cha)
print(xtabs_gender_nurse)
barplot(xtabs_gender_nurse, beside = TRUE, col = c("red", "blue","purple"))
legend("center", legend = c("man", "NO", "woman"),
       fill = c("red", "blue","purple"))

model <- polr(Nursecow~ Gender1, data = cha_mf, Hess=TRUE)
summary(model)
summary_model <- summary(model)
z_value_gender1woman <- summary_model$coefficients["Gender1Woman", "t value"]
p_value_gender1woman <- 2 * (1 - pnorm(abs(z_value_gender1woman)))
print(p_value_gender1woman)

#overall p value = 0.35

```

### Ideal by Age

Dichotomized age to be "young" = 25-35, 36-45; "old"=over 46

```{r}

#Individual

# Using xtabs()
xtabs_time_indv <- xtabs(~ Age1 + Indv, cha)
# Display the tables
print(xtabs_time_indv)

model <- polr(Indv~ Age1, data = cha_mf, Hess=TRUE)
summary(model)
summary_model <- summary(model)
z_value_age <- summary_model$coefficients["Age1young", "t value"]
p_value_age <- 2 * (1 - pnorm(abs(z_value_age)))
print(p_value_age)

#P = 0.07

#Pair
xtabs_time_pair <- xtabs(~ Age1 + Pair, cha)
print(xtabs_time_pair)

model <- polr(Pair~ Age1, data = cha_mf, Hess=TRUE)
summary(model)
summary_model <- summary(model)
z_value_age <- summary_model$coefficients["Age1young", "t value"]
p_value_age <- 2 * (1 - pnorm(abs(z_value_age)))
print(p_value_age)

# P = 0.052


#Small Group
xtabs_time_small <- xtabs(~ Age1 + SmGrp, cha)
print(xtabs_time_small)

model <- polr(SmGrp~ Age1, data = cha_mf, Hess=TRUE)
summary(model)
summary_model <- summary(model)
z_value_age <- summary_model$coefficients["Age1young", "t value"]
p_value_age <- 2 * (1 - pnorm(abs(z_value_age)))
print(p_value_age)

#P = 0.28


#Large Group
xtabs_time_large <- xtabs(~ Age1 + LargeGrp, cha)
print(xtabs_time_large)

model <- polr(LargeGrp~ Age1, data = cha_mf, Hess=TRUE)
summary(model)
summary_model <- summary(model)
z_value_age <- summary_model$coefficients["Age1young", "t value"]
p_value_age <- 2 * (1 - pnorm(abs(z_value_age)))
print(p_value_age)

#P = 0.71


#Dam
xtabs_time_dam <- xtabs(~ Age1 + Dam, cha)
print(xtabs_time_dam)

model <- polr(Dam~ Age1, data = cha_mf, Hess=TRUE)
summary(model)
summary_model <- summary(model)
z_value_age <- summary_model$coefficients["Age1young", "t value"]
p_value_age <- 2 * (1 - pnorm(abs(z_value_age)))
print(p_value_age)

#P = 0.58


#Nurse Cow
xtabs_time_nurse <- xtabs(~ Age1 + Nursecow, cha)
print(xtabs_time_nurse)

model <- polr(Nursecow~ Age1, data = cha_mf, Hess=TRUE)
summary(model)
summary_model <- summary(model)
z_value_age <- summary_model$coefficients["Age1young", "t value"]
p_value_age <- 2 * (1 - pnorm(abs(z_value_age)))
print(p_value_age)

#P = 0.12




```

### Ideal by Country

```{r}

#Individual

# Using xtabs()
xtabs_usa_indv <- xtabs(~ Country + Indv, cha)
# Display the tables
print(xtabs_usa_indv)
barplot(xtabs_usa_indv, beside = TRUE, col = c(2, 4))
legend("center", legend = c("CAN", "US"),
       fill = c(2, 4))

model <- polr(Indv~ Country, data = cha_mf, Hess=TRUE)
summary(model)
summary_model <- summary(model)
z_value_usa <- summary_model$coefficients["CountryUS", "t value"]
p_value_usa <- 2 * (1 - pnorm(abs(z_value_usa)))
print(p_value_usa)

#P = 0.009


#Pair
xtabs_usa_pair <- xtabs(~ Country + Pair, cha)
print(xtabs_usa_pair)
barplot(xtabs_usa_pair, beside = TRUE, col = c(2, 4))
legend("center", legend = c("CAN", "US"),
       fill = c(2, 4))

model <- polr(Indv~ Country, data = cha_mf, Hess=TRUE)
summary(model)
summary_model <- summary(model)
z_value_usa <- summary_model$coefficients["CountryUS", "t value"]
p_value_usa <- 2 * (1 - pnorm(abs(z_value_age)))
print(p_value_usa)

#P = 0.12


#Small Group
xtabs_usa_small <- xtabs(~ Country + SmGrp, cha)
print(xtabs_usa_small)
barplot(xtabs_usa_small, beside = TRUE, col = c(2, 4))
legend("center", legend = c("CAN", "US"),
       fill = c(2, 4))

#Large Group
xtabs_usa_large <- xtabs(~ Country + LargeGrp, cha)
print(xtabs_usa_large)
barplot(xtabs_usa_large, beside = TRUE, col = c(2, 4))
legend("center", legend = c("CAN", "US"),
       fill = c(2, 4))

#Dam
xtabs_usa_dam <- xtabs(~ Country + Dam, cha)
print(xtabs_usa_dam)
barplot(xtabs_usa_dam, beside = TRUE, col = c(2, 4))
legend("center", legend = c("CAN", "US"),
       fill = c(2, 4))

#Nurse Cow
xtabs_usa_nurse <- xtabs(~ Country + Nursecow, cha)
print(xtabs_usa_nurse)
barplot(xtabs_usa_nurse, beside = TRUE, col = c(2, 4))
legend("center", legend = c("CAN", "US"),
       fill = c(2, 4))



```

### Ideal by Top Dairy

```{r}

#Individual

# Using xtabs()
xtabs_top_indv <- xtabs(~ Top10Dairy + Indv, usa)
# Display the tables
print(xtabs_top_indv)


#Pair
xtabs_top_pair <- xtabs(~ Top10Dairy + Pair, usa)
print(xtabs_top_pair)


#Small Group
xtabs_top_small <- xtabs(~ Top10Dairy + SmGrp, usa)
print(xtabs_top_small)


#Large Group
xtabs_top_large <- xtabs(~ Top10Dairy + LargeGrp, usa)
print(xtabs_top_large)


#Dam
xtabs_top_dam <- xtabs(~ Top10Dairy + Dam, usa)
print(xtabs_top_dam)

#Nurse Cow
xtabs_top_nurse <- xtabs(~ Top10Dairy + Nursecow, usa)
print(xtabs_top_nurse)




```

### Ideal by Dairy Time

```{r}

#Individual

# Using xtabs()
xtabs_time_indv <- xtabs(~ DairyTime + Indv, cha)
# Display the tables
print(xtabs_time_indv)


#Pair
xtabs_time_pair <- xtabs(~ DairyTime+ Pair, cha)
print(xtabs_time_pair)


#Small Group
xtabs_time_small <- xtabs(~ DairyTime + SmGrp, cha)
print(xtabs_time_small)


#Large Group
xtabs_time_large <- xtabs(~ DairyTime + LargeGrp, cha)
print(xtabs_time_large)


#Dam
xtabs_time_dam <- xtabs(~ DairyTime + Dam, cha)
print(xtabs_time_dam)

#Nurse Cow
xtabs_time_nurse <- xtabs(~ DairyTime + Nursecow, cha)
print(xtabs_time_nurse)

# Assuming you have an xtabs result in xtabs_table
bp <- barplot(xtabs_time_nurse, beside = TRUE, col = c("pink", "blue", "green"))

# Adding labels to the bars
legend("center", legend = c(">75%", "25 - 50%", "50 - 75%"),
       fill = c("pink", "blue", "green"))




```

### Ideal Final Models

#### Age Dichotomous

```{r}
#can we put all these in the same model? 

#INDV: Country sig, age and gender are not. 
#people from US are at a lower odds of being in a higher category (more positive for indv housing)
cha_mf$Country <- relevel(factor(cha_mf$Country), ref = "US")
cha_mf$Age1 <- relevel(factor(cha_mf$Age1), ref = "young")

model <- polr(Indv~ Gender1 + Age1 + Country, data = cha_mf, Hess=TRUE)
summary(model)

ctable <- coef(summary(model))
p <- pnorm(abs(ctable[, "t value"]), lower.tail = FALSE) * 2
(ctable <- cbind(ctable, "p value" = p))
(ci <- confint(model))
confint.default(model)
exp(coef(model))
exp(cbind(OR = coef(model), ci))

#Pair: nothing significant
model <- polr(Pair~ Gender1 + Age1 + Country, data = cha_mf, Hess=TRUE)
summary(model)

ctable <- coef(summary(model))
p <- pnorm(abs(ctable[, "t value"]), lower.tail = FALSE) * 2
(ctable <- cbind(ctable, "p value" = p))
(ci <- confint(model))
confint.default(model)
exp(coef(model))
exp(cbind(OR = coef(model), ci))

#Small Group: country yes, age and gender no
#US has higher odds of being in a higher category
model <- polr(SmGrp~ Gender1 + Age1 + Country, data = cha_mf, Hess=TRUE)
summary(model)

ctable <- coef(summary(model))
p <- pnorm(abs(ctable[, "t value"]), lower.tail = FALSE) * 2
(ctable <- cbind(ctable, "p value" = p))
(ci <- confint(model))
confint.default(model)
exp(coef(model))
exp(cbind(OR = coef(model), ci))


#Large Group: gender different, age, country no
#being a woman is associated with a higher odds of being in a higher category
model <- polr(LargeGrp~ Gender1 + Age1 + Country, data = cha_mf, Hess=TRUE)
summary(model)

ctable <- coef(summary(model))
p <- pnorm(abs(ctable[, "t value"]), lower.tail = FALSE) * 2
(ctable <- cbind(ctable, "p value" = p))
(ci <- confint(model))
confint.default(model)
exp(coef(model))
exp(cbind(OR = coef(model), ci))


#Dam: no differences
model <- polr(Dam~ Gender1 + Age1 + Country, data = cha_mf, Hess=TRUE)
summary(model)

ctable <- coef(summary(model))
p <- pnorm(abs(ctable[, "t value"]), lower.tail = FALSE) * 2
(ctable <- cbind(ctable, "p value" = p))
(ci <- confint(model))
confint.default(model)
exp(coef(model))
exp(cbind(OR = coef(model), ci))


#Nurse Cow: gender and age, country no
#Women lower odds in higher category
#youths higher odds of higher category
model <- polr(Nursecow~ Gender1 + Age1 + Country , data = cha_mf, Hess=TRUE)
summary(model)
ctable <- coef(summary(model))
p <- pnorm(abs(ctable[, "t value"]), lower.tail = FALSE) * 2
(ctable <- cbind(ctable, "p value" = p))
(ci <- confint(model))
confint.default(model)
exp(coef(model))
exp(cbind(OR = coef(model), ci))


```

#### **Age Not Dichotomous**

```{r}
#can we put all these in the same model? 

#INDV: Country sig, age and gender are not. 
#people from US are at a lower odds of being in a higher category (more positive for indv housing)

cha_mf$Country <- relevel(cha_mf$Country, ref = "CAN")

model <- polr(Indv~ Gender1 + Age + Country, data = cha_mf, Hess=TRUE)
summary(model)

ctable <- coef(summary(model))
p <- pnorm(abs(ctable[, "t value"]), lower.tail = FALSE) * 2
(ctable <- cbind(ctable, "p value" = p))
(ci <- confint(model))
confint.default(model)
exp(coef(model))
exp(cbind(OR = coef(model), ci))

#Pair: nothing significant
model <- polr(Pair~ Gender1 + Age + Country, data = cha_mf, Hess=TRUE)
summary(model)

ctable <- coef(summary(model))
p <- pnorm(abs(ctable[, "t value"]), lower.tail = FALSE) * 2
(ctable <- cbind(ctable, "p value" = p))
(ci <- confint(model))
confint.default(model)
exp(coef(model))
exp(cbind(OR = coef(model), ci))

#Small Group: country yes, age and gender no
#US has higher odds of being in a higher category
model <- polr(SmGrp~ Gender1 + Age + Country, data = cha_mf, Hess=TRUE)
summary(model)

ctable <- coef(summary(model))
p <- pnorm(abs(ctable[, "t value"]), lower.tail = FALSE) * 2
(ctable <- cbind(ctable, "p value" = p))
(ci <- confint(model))
confint.default(model)
exp(coef(model))
exp(cbind(OR = coef(model), ci))


#Large Group: gender different, age, country no
#being a woman is associated with a higher odds of being in a higher category
model <- polr(LargeGrp~ Gender1 + Age + Country, data = cha_mf, Hess=TRUE)
summary(model)

ctable <- coef(summary(model))
p <- pnorm(abs(ctable[, "t value"]), lower.tail = FALSE) * 2
(ctable <- cbind(ctable, "p value" = p))
(ci <- confint(model))
confint.default(model)
exp(coef(model))
exp(cbind(OR = coef(model), ci))


#Dam: no differences
model <- polr(Dam~ Gender1 + Age + Country, data = cha_mf, Hess=TRUE)
summary(model)

ctable <- coef(summary(model))
p <- pnorm(abs(ctable[, "t value"]), lower.tail = FALSE) * 2
(ctable <- cbind(ctable, "p value" = p))
(ci <- confint(model))
confint.default(model)
exp(coef(model))
exp(cbind(OR = coef(model), ci))


#Nurse Cow: gender and age, country no
#Women lower odds in higher category
#youths higher odds of higher category
model <- polr(Nursecow~ Gender1 + Age + Country , data = cha_mf, Hess=TRUE)
summary(model)
ctable <- coef(summary(model))
p <- pnorm(abs(ctable[, "t value"]), lower.tail = FALSE) * 2
(ctable <- cbind(ctable, "p value" = p))
(ci <- confint(model))
confint.default(model)
exp(coef(model))
exp(cbind(OR = coef(model), ci))


```

## How Acceptable? Likert Question

### Overall

```{r}

#Housing calves individually is an acceptable way to raise calves
tab1(cha$HouseIndv, cum.percent=TRUE)

#Housing calves in a pair is an acceptable way to raise calves
tab1(cha$HousePair, cum.percent=TRUE)

#Housing calves in small group is an acceptable way to raise calves
tab1(cha$HouseSmlGrp, cum.percent=TRUE)

#Housing calves in large groups is an acceptable way to raise calves
tab1(cha$HouseLrgGrp, cum.percent=TRUE)

#Housing calves with other cow calf pairs acceptable way to raise calves
tab1(cha$WithDam, cum.percent=TRUE)

#Housing calves with nurse cows acceptable way to raise calves
tab1(cha$WithNurse, cum.percent=TRUE)

#Attention question: I am a vet (100% of sample should agree)
tab1(cha$VET, cum.percent=TRUE)





```

### Acceptable by Gender1

```{r}

#Individual

# Using xtabs()
xtabs_acc_indv <- xtabs(~ Gender1 + HouseIndv, cha)
# Display the tables
print(xtabs_acc_indv)

barplot(xtabs_acc_indv, beside = TRUE, col = c("red", "blue", "green","purple"))

# Adding labels to the bars
legend("center", legend = c("man", "non-binary", "prefer not to say", "woman"),
       fill = c("red", "blue", "green","purple"))


#Pair
xtabs_acc_pair <- xtabs(~ Gender1 + HousePair, cha)
print(xtabs_acc_pair)
barplot(xtabs_acc_pair, beside = TRUE, col = c("red", "blue", "green","purple"))
legend("center", legend = c("man", "non-binary", "prefer not to say", "woman"),
       fill = c("red", "blue", "green","purple"))

#Small Group
xtabs_acc_small <- xtabs(~ Gender1 + HouseSmlGrp, cha)
print(xtabs_acc_small)
barplot(xtabs_acc_small, beside = TRUE, col = c("red", "blue", "green","purple"))
legend("center", legend = c("man", "non-binary", "prefer not to say", "woman"),
       fill = c("red", "blue", "green","purple"))

#Large Group
xtabs_acc_large <- xtabs(~ Gender1 + HouseLrgGrp, cha)
print(xtabs_acc_large)
barplot(xtabs_acc_large, beside = TRUE, col = c("red", "blue", "green","purple"))
legend("center", legend = c("man", "non-binary", "prefer not to say", "woman"),
       fill = c("red", "blue", "green","purple"))

#Dam
xtabs_acc_dam <- xtabs(~ Gender1 + WithDam, cha)
print(xtabs_acc_dam)
barplot(xtabs_acc_dam, beside = TRUE, col = c("red", "blue", "green","purple"))
legend("center", legend = c("man", "non-binary", "prefer not to say", "woman"),
       fill = c("red", "blue", "green","purple"))

#Nurse Cow
xtabs_acc_nurse <- xtabs(~ Gender1 + WithNurse, cha)
print(xtabs_acc_nurse)
barplot(xtabs_acc_nurse, beside = TRUE, col = c("red", "blue", "green","purple"))
legend("center", legend = c("man", "non-binary", "prefer not to say", "woman"),
       fill = c("red", "blue", "green","purple"))



```

### Acceptable by Age

```{r}

#Individual

# Using xtabs()
xtabs_time_accindv <- xtabs(~ Age1 + HouseIndv, cha)
# Display the tables
print(xtabs_time_accindv)


#Pair
xtabs_time_accpair <- xtabs(~ Age1 + HousePair, cha)
print(xtabs_time_accpair)


#Small Group
xtabs_time_accsmall <- xtabs(~ Age1 + HouseSmlGrp, cha)
print(xtabs_time_accsmall)


#Large Group
xtabs_time_acclarge <- xtabs(~ Age1 + HouseLrgGrp, cha)
print(xtabs_time_acclarge)


#Dam
xtabs_time_accdam <- xtabs(~ Age1 + WithDam, cha)
print(xtabs_time_accdam)

#Nurse Cow
xtabs_time_accnurse <- xtabs(~ Age1 + WithNurse, cha)
print(xtabs_time_accnurse)




```

### Acceptable by Country

```{r}

#Individual

# Using xtabs()
xtabs_usa_accindv <- xtabs(~ Country + HouseIndv, cha)
# Display the tables
print(xtabs_usa_accindv)
barplot(xtabs_usa_accindv, beside = TRUE, col = c(2, 4))
legend("center", legend = c("CAN", "US"),
       fill = c(2, 4))


#Pair
xtabs_usa_accpair <- xtabs(~ Country + HousePair, cha)
print(xtabs_usa_accpair)
barplot(xtabs_usa_accpair, beside = TRUE, col = c(2, 4))
legend("center", legend = c("CAN", "US"),
       fill = c(2, 4))

#Small Group
xtabs_usa_accsmall <- xtabs(~ Country + HouseSmlGrp, cha)
print(xtabs_usa_accsmall)
barplot(xtabs_usa_accsmall, beside = TRUE, col = c(2, 4))
legend("center", legend = c("CAN", "US"),
       fill = c(2, 4))

#Large Group
xtabs_usa_acclarge <- xtabs(~ Country + HouseLrgGrp, cha)
print(xtabs_usa_acclarge)
barplot(xtabs_usa_acclarge, beside = TRUE, col = c(2, 4))
legend("center", legend = c("CAN", "US"),
       fill = c(2, 4))

#Dam
xtabs_usa_accdam <- xtabs(~ Country + WithDam, cha)
print(xtabs_usa_accdam)
barplot(xtabs_usa_accdam, beside = TRUE, col = c(2, 4))
legend("center", legend = c("CAN", "US"),
       fill = c(2, 4))

#Nurse Cow
xtabs_usa_accnurse <- xtabs(~ Country + WithNurse, cha)
print(xtabs_usa_accnurse)
barplot(xtabs_usa_accnurse, beside = TRUE, col = c(2, 4))
legend("center", legend = c("CAN", "US"),
       fill = c(2, 4))



```

### Acceptable Final Models

```{r}
#can we put all these in the same model? 

#INDV: Gender and country are significant, age is not
#What does the outcome mean? Being a woman is associated with being in a higher category (less enthusiastic about individual housing). Being from the US is associated with a lower odds of being in a higher category. 
#if the coefficient is - (associated with lower odds of begin in higher category)
#if the coefficient is + (associated with higher odds of begin in a higher category)

#So being female is associated with being less supporting of individual housing; being from US means more supportive of individual housing. 

cha_mf$Country <- relevel(factor(cha_mf$Country), ref = "US")
cha_mf$Age1 <- relevel(factor(cha_mf$Age1), ref = "young")

model <- polr(HouseIndv~ Gender1 + Age1 + Country, data = cha_mf, Hess=TRUE)
summary(model)

ctable <- coef(summary(model))
p <- pnorm(abs(ctable[, "t value"]), lower.tail = FALSE) * 2
(ctable <- cbind(ctable, "p value" = p))
(ci <- confint(model))
confint.default(model)
exp(coef(model))
exp(cbind(OR = coef(model), ci))

#Pair: Age and Country are sig, gender is not
#begin young is associated with lower odds of being in higher category (youths love pair housing)
#being from US associated with higher odds of being in a higher category (Canadians love pair housing)
model <- polr(HousePair~ Gender1 + Age1 + Country, data = cha_mf, Hess=TRUE)
summary(model)

ctable <- coef(summary(model))
p <- pnorm(abs(ctable[, "t value"]), lower.tail = FALSE) * 2
(ctable <- cbind(ctable, "p value" = p))
(ci <- confint(model))
confint.default(model)
exp(coef(model))
exp(cbind(OR = coef(model), ci))

#Small Group: gender and country yes
#being a woman associated with lower odds of being in a higher category
#being from US associated with higher odds of being in a higher category
model <- polr(HouseSmlGrp~ Gender1 + Age1 + Country, data = cha_mf, Hess=TRUE)
summary(model)

ctable <- coef(summary(model))
p <- pnorm(abs(ctable[, "t value"]), lower.tail = FALSE) * 2
(ctable <- cbind(ctable, "p value" = p))
(ci <- confint(model))
confint.default(model)
exp(coef(model))
exp(cbind(OR = coef(model), ci))


#Large Group: age yes, gender and country no
#being a young associated with have lower odds of being in higher category
model <- polr(HouseLrgGrp~ Gender1 + Age1 + Country, data = cha_mf, Hess=TRUE)
summary(model)

ctable <- coef(summary(model))
p <- pnorm(abs(ctable[, "t value"]), lower.tail = FALSE) * 2
(ctable <- cbind(ctable, "p value" = p))
(ci <- confint(model))
confint.default(model)
exp(coef(model))
exp(cbind(OR = coef(model), ci))


#Dam: no differences
model <- polr(WithDam~ Gender1 + Age1 + Country, data = cha_mf, Hess=TRUE)
summary(model)

ctable <- coef(summary(model))
p <- pnorm(abs(ctable[, "t value"]), lower.tail = FALSE) * 2
(ctable <- cbind(ctable, "p value" = p))
(ci <- confint(model))
confint.default(model)
exp(coef(model))
exp(cbind(OR = coef(model), ci))


#Nurse Cow: no differences
model <- polr(WithNurse~ Gender1 + Age1 + Country , data = cha_mf, Hess=TRUE)
summary(model)

ctable <- coef(summary(model))
p <- pnorm(abs(ctable[, "t value"]), lower.tail = FALSE) * 2
(ctable <- cbind(ctable, "p value" = p))
(ci <- confint(model))
confint.default(model)
exp(coef(model))
exp(cbind(OR = coef(model), ci))




```

## General Public Feelings

(Most and Least Acceptable)

```{r}

tab1(cha$GeneralPubMost, cum.percent=TRUE)
tab1(cha$GeneralPubLeast, cum.percent=TRUE)

#by gender
xtabs_most <- xtabs(~ Gender1 + GeneralPubMost, cha)
print(xtabs_most)
barplot(xtabs_most, beside = TRUE, col = c("red", "blue", "green","purple"))
legend("center", legend = c("man", "non-binary", "prefer not to say", "woman"),
       fill = c("red", "blue", "green","purple"))


xtabs_least <- xtabs(~ Gender1 + GeneralPubLeast, cha)
print(xtabs_least)
barplot(xtabs_least, beside = TRUE, col = c("red", "blue", "green","purple"))
legend("center", legend = c("man", "non-binary", "prefer not to say", "woman"),
       fill = c("red", "blue", "green","purple"))

#by country

xtabs_countrymost <- xtabs(~ Country + GeneralPubMost, cha)
print(xtabs_countrymost)
barplot(xtabs_countrymost, beside = TRUE, col = c(2, 4))
legend("center", legend = c("CAN", "US"),
       fill = c(2, 4))

xtabs_countryleast <- xtabs(~ Country + GeneralPubLeast, cha)
print(xtabs_countryleast)
barplot(xtabs_countryleast, beside = TRUE, col = c(2, 4))
legend("center", legend = c("CAN", "US"),
       fill = c(2, 4))

#by age
xtabs_agemost <- xtabs(~ Age1 + GeneralPubMost, cha)
print(xtabs_agemost)
barplot(xtabs_agemost, beside = TRUE, col = c(2, 4))
legend("center", legend = c("young", "old"),
       fill = c(2, 4))

xtabs_ageleast <- xtabs(~ Age1 + GeneralPubLeast, cha)
print(xtabs_ageleast)
barplot(xtabs_ageleast, beside = TRUE, col = c(2, 4))
legend("center", legend = c("young", "old"),
       fill = c(2, 4))


```

## Transition Feasibility

```{r}

tab1(cha$FeasibleINDVtoPAIR, cum.percent=TRUE)


#age, young vs old
xtabs_agefease <- xtabs(~ Age1 + FeasibleINDVtoPAIR, cha)
print(xtabs_agefease)
barplot(xtabs_agefease, beside = TRUE, col = c(2, 4))
legend("center", legend = c("young", "old"),
       fill = c(2, 4))


#Gender, male vs. female
xtabs_sexfease <- xtabs(~ Gender1 + FeasibleINDVtoPAIR, cha)
print(xtabs_sexfease)
barplot(xtabs_sexfease, beside = TRUE, col = c(2, 4))
legend("center", legend = c("man", "woman"),
       fill = c(2, 4))


#Country
xtabs_usafease <- xtabs(~ Country + FeasibleINDVtoPAIR, cha)
print(xtabs_usafease)
barplot(xtabs_usafease, beside = TRUE, col = c(2, 4))
legend("center", legend = c("US", "CAN"),
       fill = c(2, 4))

#Transition Feasibility: country yes, not age or gender
#US higher odds in being in a higher category. They hate the idea. Canadaians LOEVE it.
cha_mf$Country <- relevel(factor(cha_mf$Country), ref = "US")
cha_mf$Age1 <- relevel(factor(cha_mf$Age1), ref = "young")


model <- polr(FeasibleINDVtoPAIR~ Gender1 + Age1 + Country, data = cha_mf, Hess=TRUE)
summary(model)

ctable <- coef(summary(model))
p <- pnorm(abs(ctable[, "t value"]), lower.tail = FALSE) * 2
(ctable <- cbind(ctable, "p value" = p))
(ci <- confint(model))
confint.default(model)
exp(coef(model))
exp(cbind(OR = coef(model), ci))

```

## Clients - Social House

```{r}

tab1(cha$SocialHouse, cum.percent=TRUE)
# Using xtabs()
xtabs_socialtype <- xtabs(~ SocialHouse + SocHT, cha)
# Display the tables
print(xtabs_socialtype)
result_df <- as.data.frame(xtabs_socialtype)
print(result_df)
```

## Clients - Revert

```{r}
tab1(cha$Reverters, cum.percent=TRUE)

cha |> 
  group_by(Country, Reverters) |> 
  count()

14/(27+14)
56/(56+58)

# Using xtabs()
xtabs_revertertype <- xtabs(~ Reverters + HouseType, cha)
# Display the tables
print(xtabs_revertertype)
result_df <- as.data.frame(xtabs_revertertype)
print(result_df)

#Reverters by country
xtabs_usarevert <- xtabs(~ Country + Reverters, cha)
print(xtabs_usarevert)
barplot(xtabs_usarevert, beside = TRUE, col = c(2, 4))
legend("center", legend = c("CAN", "US"),
       fill = c(2, 4))
```

## Most Common 20y

```{r}

tab1(cha$MostComm20y, cum.percent=TRUE)
tab1(usa$MostComm20y, cum.percent=TRUE)
tab1(canada$MostComm20y, cum.percent=TRUE)

xtabs_common <- xtabs(~ Age1 + MostComm20y, cha)
print(xtabs_common)

xtabs_common <- xtabs(~ Gender1 + MostComm20y, cha)
print(xtabs_common)

xtabs_common <- xtabs(~ DairyRegion + MostComm20y, cha)
print(xtabs_common)

cha_mf$Country <- relevel(factor(cha_mf$Country), ref = "US")
cha_mf$Age1 <- relevel(factor(cha_mf$Age1), ref = "young")

#Most Common in 20years: no differences, but not sure this is the right way to handle this data? 
model <- polr(MostComm20y~ Gender1 + Age1 + Country , data = cha_mf, method="logistic", Hess=TRUE)
summary(model)
logLik(model)
pR2(model)

ctable <- coef(summary(model))
p <- pnorm(abs(ctable[, "t value"]), lower.tail = FALSE) * 2
(ctable <- cbind(ctable, "p value" = p))
(ci <- confint(model))
confint.default(model)
exp(coef(model))
exp(cbind(OR = coef(model), ci))


```

## New Stacked Bar Charts for Pub

### Most and Least Ideal

```{r}

df <- data.frame(
  Group = c("Individual", "Pair (n=2)", "Small Group (n=3-8)", 
            "Large Group (n>8)", "With Dam", "With Nurse Cow"),
  Most_Ideal = c(48, 28, 15, 1, 6, 1),
  Ideal_2 = c(17, 52, 16, 6, 4, 5),
  Ideal_3 = c(16, 8, 54, 10, 5, 8),
  Ideal_4 = c(9, 6, 8, 59, 10, 8),
  Ideal_5 = c(4, 5, 7, 4, 49, 32),
  Least_Ideal = c(6, 1, 0, 20, 26, 46)
)

df_long <- df |> 
  pivot_longer(cols = -Group, names_to = "Rating", values_to = "Percentage")

df_long$Group <- factor(df_long$Group, levels = rev(df$Group))  
df_long$Rating <- factor(df_long$Rating, 
                         levels = rev(c("Most_Ideal", "Ideal_2", "Ideal_3", 
                                        "Ideal_4", "Ideal_5", "Least_Ideal")))


ggplot(df_long, aes(x = Percentage, y = Group, fill = Rating)) +
  geom_bar(stat = "identity", position = "stack", color = "black") +
      geom_text(
        aes(label = ifelse(Percentage > 1, Percentage, "")),
            position = position_stack(vjust = 0.5), 
            color = "black", size = 3.5, 
            family = "Times New Roman") + 
    scale_fill_manual(values = c(
              "Most_Ideal" = "grey99",
              "Ideal_2" =  "grey91", 
              "Ideal_3" = "grey83", 
              "Ideal_4" = "grey75",
              "Ideal_5" = "grey67",
              "Least_Ideal"= "grey59"),
                    labels = c("Least Ideal", "", "", "", "", "Most Ideal"), 
                     guide = guide_legend(nrow = 1, reverse=TRUE)) +  
  labs(x = "Percentage of Respondents (%)", y = "", fill = "") +
  theme_classic()+
  theme (legend.position = "none", 
         legend.direction = "horizontal", 
              axis.text = element_text(color = "black", size=10), 
               legend.text = element_text(color = "black", size=10))+
                theme(text=element_text(size=10, family = "Times New Roman"))

```

```{r}
df <- data.frame(
  Group = c("Individual", "Pair (n=2)", "Small Group (n=3-8)", 
            "Large Group (n>8)", "With Dam", "With Nurse Cow"),
  Most_Ideal = c(48, 28, 15, 1, 6, 1),
  Ideal_2 = c(17, 52, 16, 6, 4, 5),
  Ideal_3 = c(16, 8, 54, 10, 5, 8),
  Ideal_4 = c(9, 6, 8, 59, 10, 8),
  Ideal_5 = c(4, 5, 7, 4, 49, 32),
  Least_Ideal = c(6, 1, 0, 20, 26, 46)
)

df_long <- df |> 
  pivot_longer(cols = -Group, names_to = "Rating", values_to = "Percentage")

df_long$Group <- factor(df_long$Group, levels = rev(df$Group))  
df_long$Rating <- factor(df_long$Rating, 
                         levels = rev(c("Most_Ideal", "Ideal_2", "Ideal_3", 
                                        "Ideal_4", "Ideal_5", "Least_Ideal")))


ggplot(df_long, aes(x = Percentage, y = Group, fill = Rating)) +
  geom_bar(stat = "identity", position = "stack", color = "black") +
      geom_text(
        aes(label = ifelse(Percentage > 1, Percentage, "")),
            position = position_stack(vjust = 0.5), 
            color = "black", size = 3.5, 
            family = "Times New Roman") + 
    scale_fill_manual(values = c(
              "Most_Ideal" = "grey99",
              "Ideal_2" =  "grey91", 
              "Ideal_3" = "grey83", 
              "Ideal_4" = "grey75",
              "Ideal_5" = "grey67",
              "Least_Ideal"= "grey59"),
                    labels = c("Least Ideal", "", "", "", "", "Most Ideal"), 
                     guide = guide_legend(nrow = 1, reverse=TRUE)) +  
  labs(x = "Percentage of Respondents (%)", y = "", fill = "") +
  theme_classic()+
  theme (legend.position = "none", 
         legend.direction = "horizontal", 
              axis.text = element_text(color = "black", size=10), 
               legend.text = element_text(color = "black", size=10))+
                theme(text=element_text(size=10, family = "Times New Roman"))



scale_fill_manual(values = c(
              "Most_Ideal" = "seashell",
              "Ideal_2" =  "lightblue1", 
              "Ideal_3" = "lightskyblue", 
              "Ideal_4" = "deepskyblue2",
              "Ideal_5" = "deepskyblue3",
              "Least_Ideal"= "deepskyblue4"),
              
              scale_fill_manual(values = c(
              "Most_Ideal" = "grey99",
              "Ideal_2" =  "grey89", 
              "Ideal_3" = "grey79", 
              "Ideal_4" = "grey69",
              "Ideal_5" = "grey59",
              "Least_Ideal"= "grey52")
              
                scale_fill_manual(values = c(
              "Most_Ideal" = "white",
              "Ideal_2" =  "cadetblue1", 
              "Ideal_3" = "cadetblue2", 
              "Ideal_4" = "cadetblue3",
              "Ideal_5" = "cadetblue",
              "Least_Ideal"= "cadetblue4")
              
               scale_fill_manual(values = c(
              "Most_Ideal" = "#55C667FF",
              "Ideal_2" =  "#73D055FF", 
              "Ideal_3" = "#95D840FF", 
              "Ideal_4" = "#B8DE29FF",
              "Ideal_5" = "#DCE319FF",
              "Least_Ideal"= "#FDE725FF")
```

### How Acceptable?

```{r}
df <- data.frame(
  Group = c("Individual", "Pair (n=2)", "Small Group (n=3-8)", 
            "Large Group (n>8)", "With Dam", "With Nurse Cow"),
  Strongly_Agree = c(64, 65, 51, 13, 15, 12),
  Somewhat_Agree = c(23, 27, 33, 31, 14, 19),
  Neutral = c(3, 4, 8, 16, 22, 19),
  Somewhat_Disagree = c(8, 3, 6, 28, 26, 28),
  Strongly_Disagree = c(2, 1, 2, 12, 23, 22))


df_long <- df |> 
  pivot_longer(cols = -Group, names_to = "Rating", values_to = "Percentage")

df_long$Group <- factor(df_long$Group, levels = rev(df$Group))  
df_long$Rating <- factor(df_long$Rating, 
                         levels = rev(c("Strongly_Agree", "Somewhat_Agree",                                  "Neutral", "Somewhat_Disagree", "Strongly_Disagree")))

ggplot(df_long, aes(x = Percentage, y = Group, fill = Rating)) +
  geom_bar(stat = "identity", position = "stack", color = "black") +
      geom_text(
        aes(label = ifelse(Percentage > 1, Percentage, "")),
            position = position_stack(vjust = 0.5), 
            color = "black", size = 3.5, 
            family = "Times New Roman") + 
    scale_fill_manual(values = c(
              "Strongly_Agree" = "grey99",
              "Somewhat_Agree" =  "grey89", 
              "Neutral" = "grey79", 
              "Somewhat_Disagree" = "grey69",
              "Strongly_Disagree" = "grey59"),
                    labels = c("Strongly Disagree", "", "", "", "", "Strongly Agree"), 
                     guide = guide_legend(nrow = 1, reverse=TRUE)) +  
  labs(x = "Percentage of Respondents (%)", y = "", fill = "") +
  theme_classic()+
  theme (legend.position = "none", 
         legend.direction = "horizontal", 
              axis.text = element_text(color = "black", size=10), 
               legend.text = element_text(color = "black", size=10))+
                theme(text=element_text(size=10, family = "Times New Roman"))



```
